---
title: 'Exercise: Linear Multilevel Models'
author: "Paul Bürkner"
date: "`r Sys.Date()`"
output: html_document
encoding: UTF-8
---

```{r, SETTINGS-knitr, include=FALSE}
# only relevant when knitting the document
options(width = 90)
knitr::opts_chunk$set(
  cache = FALSE,
  comment = NA,
  message = FALSE,
  warning = FALSE
)
```

Load required packages:
```{r, cache=FALSE}
library(brms)
```

## Example: Sleepstudy

Load the data:
```{r}
data("sleepstudy", package = "lme4")
head(sleepstudy)
# look at the help page:
# ?sleepstudy
```

Preparation of data we need later for conditional plots

```{r}
conditions <- make_conditions(sleepstudy, "Subject")
```

### Analyse the data

Fit a complete pooling model:
```{r, results="hide"}
fit_sleep1 <- brm(Reaction ~ 1 + Days, data = sleepstudy)
```

Summarize results:
```{r}
summary(fit_sleep1)
plot(fit_sleep1, ask = FALSE)
```

Vizualize predictions:
```{r}
plot(conditional_effects(fit_sleep1), points = TRUE)
```

Compute fitted values and residuals
```{r}
head(fitted(fit_sleep1))
head(residuals(fit_sleep1))
```

Check model fit:
```{r}
pp_check(fit_sleep1)
pp_check(fit_sleep1, "error_scatter_avg")
```

partial pooling: individual intercept, common slope:
```{r, results="hide"}
fit_sleep2 <- brm(Reaction ~ 1 + Days + (1 | Subject), 
                  data = sleepstudy)
```

```{r}
summary(fit_sleep2)
plot(fit_sleep2)
```

Extract effects of each Subject:
```{r}
coef(fit_sleep2)
```

Visualize predictions:
```{r}
plot(conditional_effects(fit_sleep2), points = TRUE)
# re_formula = NULL ensures that group-level effects are included
me2 <- conditional_effects(fit_sleep2, conditions = conditions, 
                        re_formula = NULL)
plot(me2, ncol = 6, points = TRUE)
```

Partial pooling: individual intercept AND slope:
```{r, results="hide"}
fit_sleep3 <- brm(
  Reaction ~ 1 + Days + (1 + Days | Subject), 
  data = sleepstudy
)
```

```{r}
summary(fit_sleep3)
plot(fit_sleep3, N = 3, ask = FALSE)
```

Extract effects of each Subject:
```{r}
coef(fit_sleep3)
```

Check model fit:
```{r}
pp_check(fit_sleep3)
pp_check(fit_sleep3, "error_scatter_avg")
```

Visualize predictions:
```{r}
plot(conditional_effects(fit_sleep3), points = TRUE)
# re_formula = NULL ensures that group-level effects are included
me3 <- conditional_effects(fit_sleep3, conditions = conditions, 
                           re_formula = NULL)
plot(me3, ncol = 6, points = TRUE)
```

Compare all trhee models:
```{r}
loo(fit_sleep1, fit_sleep2, fit_sleep3)
```

Compute model weights:
```{r}
model_weights(fit_sleep1, fit_sleep2, fit_sleep3, weights = "loo")
```

### Working with priors

Find out on which parameters to set priors:
```{r}
get_prior(Reaction ~ 1 + Days + (1 + Days | Subject), 
          data = sleepstudy)
```

Let's define some priors:
```{r}
bprior <- c(set_prior("normal(5, 5)", coef = "Days"),
            set_prior("cauchy(0, 10)", class = "sd"),
            set_prior("lkj(2)", class = "cor"))
bprior
```

Fit the partial pooling model again with these priors. Also sample from these priors.

```{r, results="hide"}
fit_sleep4 <- brm(
  Reaction ~ 1 + Days + (1 + Days | Subject), 
  data = sleepstudy, prior = bprior, 
  sample_prior = TRUE
)
```

```{r}
summary(fit_sleep4)
```


### Evaluate some hypothesis

```{r}
# Evid.Ratio is the ratio of P(Days > 7) / P(Days <= 7)
(hyp1 <- hypothesis(fit_sleep4, "Days < 7"))
plot(hyp1)
```

```{r}
# Evid.Ratio is the Bayes Factor of the posterior
# vs the prior that Days = 10 is TRUE (Savage-Dickey Ratio)
(hyp2 <- hypothesis(fit_sleep4, "Days = 10"))
plot(hyp2)
```

Excerise: Try out other post-processing methods yourself:
```{r}
methods(class = "brmsfit")
```
